Reflections from reproductions

### 2024-10-17 pages/reflections.qmd
docs(reflections): add note about hernandez 2015 local dependency

@hernandez_optimal_2015: Partially met. Some (but not all) of the required packages were listed in the paper.

@@

* The `import` statements can be sufficient in indicating all the packages required but this is not always the case if there are "hidden"/unmentioned dependencies that don't get imported
* There are various options for listing the packages (e.g. comprehensive import statements, installation lines in the script, environment files).
* Ideally mention this in repository, not just the paper.
* This was a common issue.

>>>>

@hernandez_optimal_2015: Partially met. Some (but not all) of the required packages were listed in the paper. Of particular note, this depended on having a local package `myutils/`, which was another GitHub repository from the author. This was not mentioned anywhere, and so required to notice this was needed.

@@

* The `import` statements can be sufficient in indicating all the packages required but this is not always the case if there are "hidden"/unmentioned dependencies that don't get imported
* There are various options for listing the packages (e.g. comprehensive import statements, installation lines in the script, environment files).
* Ideally mention this in repository, not just the paper.
* If there are local dependencies (e.g. other GitHub repositories), make sure to (a) mention and link to these repositories, so it is clear they are also required, and (b) include license/s in those repositories also, so they can be used.
* This was a common issue.
